Title Goes Here

### 2021-04-07 analysis/paper/shceof.Rmd
Arregla r2 negativo (estaba mostrando r)
Closes #11

The Imaginary cEOF2 is related with the SAM through the A-SAM in the troposphere, with up to \textcolor{red}{(Acá aparece un -)} `r scales::percent(max_r2[cEOF == "cEOF2"]$estimate, 2)` of shared variance, reached at `r max_r2[cEOF == "cEOF2"]$lev` hPa (Figure\ \@ref(fig:sam-eof-vertical).b2).

>>>>

The Imaginary cEOF2 is related with the SAM through the A-SAM in the troposphere, with up to `r scales::percent(max_r2[cEOF == "cEOF2"]$estimate^2, 2)` of shared variance, reached at `r max_r2[cEOF == "cEOF2"]$lev` hPa (Figure\ \@ref(fig:sam-eof-vertical).b2).
